# Lab Sheet 4

First, we read in our data:
```{r}
data_A <- read.table("https://people.bath.ac.uk/kai21/ASI/data/Lab4_data_A.txt")
data_B <- read.table("https://people.bath.ac.uk/kai21/ASI/data/Lab4_data_B.txt")
```

## Normal distribution

We define functions to input into optim as our gradient + loglikelihood
```{r}
# exp ensures nu > 0 
expr_normal <- 
  expression(
    (y - theta1 - theta2 * x) ^ 2 / (2 * exp(theta3)) + log(2 * pi * exp(theta3)) / 2
  )

normal_aux <- deriv(expr_normal, c("theta1", "theta2", "theta3"), function.arg = c("theta1", "theta2", "theta3", "x", "y"), hessian = F)

normal_nll <- function(theta, data) {
  res <- normal_aux(theta[1], theta[2], theta[3], data$x, data$y)
  
  sum(as.numeric(res)) 
}

normal_grad <- function(theta, data) {
  res <- normal_aux(theta[1], theta[2], theta[3], data$x, data$y)
  
  apply(attr(res, "gradient"), 2, sum)
}
```

Now, use optim to approximate data A and plot result
```{r}
normal_fit_A <- NULL

normal_fit_A[[1]] <- 
  optim(
    par = c(0.5, 2, 3),
    fn = normal_nll,
    gr = normal_grad,
    method = 'BFGS',
    data = data_A
  )

normal_fit_A[[2]] <- 
  optim(
    par = c(2, 0.5, 5),
    fn = normal_nll,
    gr = normal_grad,
    method = 'BFGS',
    data = data_A
  )

if(normal_fit_A[[1]]$value < normal_fit_A[[2]]$value) {
  theta1 <- normal_fit_A[[1]]$par[[1]]
  theta2 <- normal_fit_A[[1]]$par[[2]]
  nu <- exp(normal_fit_A[[1]]$par[[3]])
} else {
  theta1 <- normal_fit_A[[2]]$par[[1]]
  theta2 <- normal_fit_A[[2]]$par[[2]]
  nu <- exp(normal_fit_A[[2]]$par[[3]])
}

normal_mu_A <- theta1 + theta2 * data_A$x

ggplot2::ggplot() +
  ggplot2::geom_point(
    data = data_A,
    ggplot2::aes(
      x = x, y = y
    )
  ) +
  ggplot2::geom_line(
    ggplot2::aes(
      x = data_A$x, y = normal_mu_A
    )
  ) +
  ggplot2::theme_minimal() +
  ggplot2::labs(
    title = "Normal Approximation To Dataset 1"
  )
```

And do the same for data B
```{r}
normal_fit_B <- NULL

normal_fit_B[[1]] <- 
  optim(
    par = c(0.5, 2, 3),
    fn = normal_nll,
    gr = normal_grad,
    method = 'BFGS',
    data = data_B
  )

normal_fit_B[[2]] <- 
  optim(
    par = c(2, 0.5, 5),
    fn = normal_nll,
    gr = normal_grad,
    method = 'BFGS',
    data = data_B
  )

if(normal_fit_B[[1]]$value < normal_fit_B[[2]]$value) {
  theta1 <- normal_fit_B[[1]]$par[[1]]
  theta2 <- normal_fit_B[[1]]$par[[2]]
  nu <- exp(normal_fit_B[[1]]$par[[3]])
} else {
  theta1 <- normal_fit_B[[2]]$par[[1]]
  theta2 <- normal_fit_B[[2]]$par[[2]]
  nu <- exp(normal_fit_B[[2]]$par[[3]])
}

normal_mu_B <- theta1 + theta2 * data_B$x

ggplot2::ggplot() +
  ggplot2::geom_point(
    data = data_B,
    ggplot2::aes(
      x = x, y = y
    )
  ) +
  ggplot2::geom_line(
    ggplot2::aes(
      x = data_B$x, y = normal_mu_B
    )
  ) +
  ggplot2::theme_minimal() +
  ggplot2::labs(
    title = "Normal Approximation To Dataset 2"
  )
```

We now want to repeat process for logistic and T-distributions

## Logistic distribution

Define functions
```{r}
# exp ensures nu > 0 
expr_logistic <- 
  expression(
    (y - theta1 - theta2 * x) / exp(theta3) + theta3 + 2 * log(1 + exp(- (y - theta1 - theta2 * x) / exp(theta3)))
  )

logistic_aux <- deriv(expr_logistic, c("theta1", "theta2", "theta3"), function.arg = c("theta1", "theta2", "theta3", "x", "y"), hessian = F)

logistic_nll <- function(theta, data) {
  res <- logistic_aux(theta[1], theta[2], theta[3], data$x, data$y)
  
  sum(as.numeric(res)) 
}

logistic_grad <- function(theta, data) {
  res <- logistic_aux(theta[1], theta[2], theta[3], data$x, data$y)
  
  apply(attr(res, "gradient"), 2, sum)
}
```

Approximate data A
```{r}
logistic_fit_A <- NULL

logistic_fit_A[[1]] <- 
  optim(
    par = c(0.5, 2, 3),
    fn = logistic_nll,
    gr = logistic_grad,
    method = 'BFGS',
    data = data_A
  )

logistic_fit_A[[2]] <- 
  optim(
    par = c(2, 0.5, 5),
    fn = logistic_nll,
    gr = logistic_grad,
    method = 'BFGS',
    data = data_A
  )

if(logistic_fit_A[[1]]$value < logistic_fit_A[[2]]$value) {
  theta1 <- logistic_fit_A[[1]]$par[[1]]
  theta2 <- logistic_fit_A[[1]]$par[[2]]
  nu <- exp(logistic_fit_A[[1]]$par[[3]])
} else {
  theta1 <- logistic_fit_A[[2]]$par[[1]]
  theta2 <- logistic_fit_A[[2]]$par[[2]]
  nu <- exp(logistic_fit_A[[2]]$par[[3]])
}

logistic_mu_A <- theta1 + theta2 * data_A$x

ggplot2::ggplot() +
  ggplot2::geom_point(
    data = data_A,
    ggplot2::aes(
      x = x, y = y
    )
  ) +
  ggplot2::geom_line(
    ggplot2::aes(
      x = data_A$x, y = logistic_mu_A
    )
  ) +
  ggplot2::theme_minimal() +
  ggplot2::labs(
    title = "Logistic Approximation To Dataset 1"
  )
```

Approximate data B
```{r}
logistic_fit_B <- NULL

logistic_fit_B[[1]] <- 
  optim(
    par = c(0.5, 2, 3),
    fn = logistic_nll,
    gr = logistic_grad,
    method = 'BFGS',
    data = data_B
  )

logistic_fit_B[[2]] <- 
  optim(
    par = c(2, 0.5, 5),
    fn = logistic_nll,
    gr = logistic_grad,
    method = 'BFGS',
    data = data_B
  )

if(logistic_fit_B[[1]]$value < logistic_fit_B[[2]]$value) {
  theta1 <- logistic_fit_B[[1]]$par[[1]]
  theta2 <- logistic_fit_B[[1]]$par[[2]]
  nu <- exp(logistic_fit_B[[1]]$par[[3]])
} else {
  theta1 <- logistic_fit_B[[2]]$par[[1]]
  theta2 <- logistic_fit_B[[2]]$par[[2]]
  nu <- exp(logistic_fit_B[[2]]$par[[3]])
}

logistic_mu_B <- theta1 + theta2 * data_A$x

ggplot2::ggplot() +
  ggplot2::geom_point(
    data = data_B,
    ggplot2::aes(
      x = x, y = y
    )
  ) +
  ggplot2::geom_line(
    ggplot2::aes(
      x = data_B$x, y = logistic_mu_B
    )
  ) +
  ggplot2::theme_minimal() +
  ggplot2::labs(
    title = "Logistic Approximation To Dataset 2"
  )
```


## T-distribution

Define functions
```{r}
# exp(theta3) + 2 ensures nu > 2
expr_tdist <- 
  expression(
    - lgamma((exp(theta3) + 3) / 2) + log(pi * (exp(theta3) + 2)) / 2 + lgamma(exp(theta3) / 2 + 1) + (exp(theta3) + 3) / 2 * log(1 + (y - theta1 - theta2 * x) ^ 2 / (exp(theta3) + 2))
  )

tdist_aux <- deriv(expr_tdist, c("theta1", "theta2", "theta3"), function.arg = c("theta1", "theta2", "theta3", "x", "y"), hessian = F)

tdist_nll <- function(theta, data) {
  res <- tdist_aux(theta[1], theta[2], theta[3], data$x, data$y)
  
  sum(as.numeric(res)) 
}

tdist_grad <- function(theta, data) {
  res <- tdist_aux(theta[1], theta[2], theta[3], data$x, data$y)
  
  apply(attr(res, "gradient"), 2, sum)
}
```

Approximate data A
```{r}
tdist_fit_A <- NULL

tdist_fit_A[[1]] <- 
  optim(
    par = c(0.5, 2, 3),
    fn = tdist_nll,
    gr = tdist_grad,
    method = 'BFGS',
    data = data_A
  )

tdist_fit_A[[2]] <- 
  optim(
    par = c(2, 0.5, 5),
    fn = tdist_nll,
    gr = tdist_grad,
    method = 'BFGS',
    data = data_A
  )

if(tdist_fit_A[[1]]$value < tdist_fit_A[[2]]$value) {
  theta1 <- tdist_fit_A[[1]]$par[[1]]
  theta2 <- tdist_fit_A[[1]]$par[[2]]
  nu <- exp(tdist_fit_A[[1]]$par[[3]]) + 2
} else {
  theta1 <- tdist_fit_A[[2]]$par[[1]]
  theta2 <- tdist_fit_A[[2]]$par[[2]]
  nu <- exp(tdist_fit_A[[2]]$par[[3]]) + 2
}

tdist_mu_A <- theta1 + theta2 * data_A$x

ggplot2::ggplot() +
  ggplot2::geom_point(
    data = data_A,
    ggplot2::aes(
      x = x, y = y
    )
  ) +
  ggplot2::geom_line(
    ggplot2::aes(
      x = data_A$x, y = tdist_mu_A
    )
  ) +
  ggplot2::theme_minimal() +
  ggplot2::labs(
    title = "T-Distribution Approximation To Dataset 1"
  )
```

Approximate data B
```{r}
tdist_fit_B <- NULL

tdist_fit_B[[1]] <- 
  optim(
    par = c(0.5, 2, 3),
    fn = tdist_nll,
    gr = tdist_grad,
    method = 'BFGS',
    data = data_B
  )

tdist_fit_B[[2]] <- 
  optim(
    par = c(2, 0.5, 5),
    fn = tdist_nll,
    gr = tdist_grad,
    method = 'BFGS',
    data = data_B
  )

if(tdist_fit_B[[1]]$value < tdist_fit_B[[2]]$value) {
  theta1 <- tdist_fit_B[[1]]$par[[1]]
  theta2 <- tdist_fit_B[[1]]$par[[2]]
  nu <- exp(tdist_fit_B[[1]]$par[[3]]) + 2
} else {
  theta1 <- tdist_fit_B[[2]]$par[[1]]
  theta2 <- tdist_fit_B[[2]]$par[[2]]
  nu <- exp(tdist_fit_B[[2]]$par[[3]]) + 2
}

tdist_mu_B <- theta1 + theta2 * data_B$x

ggplot2::ggplot() +
  ggplot2::geom_point(
    data = data_B,
    ggplot2::aes(
      x = x, y = y
    )
  ) +
  ggplot2::geom_line(
    ggplot2::aes(
      x = data_B$x, y = tdist_mu_B
    )
  ) +
  ggplot2::theme_minimal() +
  ggplot2::labs(
    title = "T-Distribution Approximation To Dataset 2"
  )
```

